High-resolution ALMA observations of V4046\,Sgr: a circumbinary disc with a thin ring

### 2021-01-20 Draft_V4046Sgr_mnras.tex
SC edits

% Abstract of the paper
\begin{abstract}
  The nearby V4046\,Sgr spectroscopic binary hosts a gas-rich disc known for its wide cavity and dusty ring.  We present high resolution ($\sim$20--50\,mas **** WRONG UPDATE TO CORRECT NUMBERS****) ALMA observations of the 1.3\,mm  continuum which, combined with SPHERE-IRDIS polarized images and a well-sampled spectral energy distribution (SED), allow us to propose a physical model for the source using radiative transfer (RT) predictions. The new ALMA data reveal a very thin ring at a radius of 13.32$\pm$0.26\,au (Ring13), with a marginally resolved radial width of 1.50$\pm$0.72\,au. Ring13 is surrounded by a $\sim$10\,au-wide gap, and it is flanked by a very mm-bright outer ring (Ring24) with a sharp inner edge at 24\,au. The intensity plateau in Ring24 breaks at $\sim$35\,au, where it steeply drops  and  extends into  a shallow tail. A compact source of mm-continuum at  the stellar position is picked up by ALMA, with a radius of ***RADIUS OF THE BLOB, IS IT RESOLVED?***.  In order to reproduce the SED in the IR, our RT model  requires an  inner circumbinary disc ***GIVE RADII*** rich in small grains (as in previous  models of V4046\,Sgr), and  which  matches the  central ALMA signal if it contains **Xxx*** Mearths in large dust. An inner  ring at $\sim$6\,au (Ring6) composed of small  grains, with a gas mass of ***Mearth*** and deprived of large dust, is required to explain the ***10$\mu$m ???*** flux density. The surprisingly thin Ring13 is nonetheless $\sim$5 times wider ****NOT CONSISTENT WITH CONCLUSIONS*** in the ALMA signal  than the model scale height, and $\sim$3***???*** narrower than the model gas radial width. Ring13 could thus be   long-lived and shaped by radial dust trapping, which would require a turbulence value of  $\alpha_{\rm turb} \sim 0.01$.   The strong near-far disc asymmetry at 1.65\,$\micron$ points at a very forward-scattering phase function, and requires grain radii of no less than 0.4\,$\micron$. The previously reported scattered-light shadow of the secondary star is also reproduced by the RADMC3D RT package. 
\end{abstract}

@@

V4046\,Sgr is a double-lined spectroscopic binary of K-type stars (K5 and K7) with very similar masses of 0.90$\pm$0.05\,M$_{\sun}$ and 0.85$\pm$0.04\,M$_{\sun}$ \citep{Rosenfeld_2012}, on a close ($a \approx 0.041$\,au), circular ($e\leq0.01$) orbit, with an orbital period of 2.42 days \citep{2000IAUS..200P..28Q}. It is a member of the $\beta$ Pictoris moving group \citep{Zuckerman_2004}, with an estimated age of 23$\pm$3\,Myr \citep{Mamajek_2014}, and its distance is 72.41$\pm$0.34\,pc \citep{Gaia}. V4046\,Sgr hosts a massive ($\sim$0.1\,M$_{\sun}$) circumbinary disc extending to $\sim$300\,au \citep{Rosenfeld_2013, Rodriguez_2010},  rich in diverse molecular lines \citep{Kastner_2018}.

@@

Image synthesis of the ALMA continuum was performed with  the {\tt uvmem} package \citep{2006ApJ...639..951C, 2018A&C....22...16C}, which fits a non-parametric model image $I^m_j$ to the data by comparing the  observed  and model visibilities, $V^\circ_k$ and $V^m_k$, using a least-squares figure of merit $L$:
\begin{equation}
  L = \sum_{k=1}^N \omega_k  |V^\circ_k - V^m_k|^2 - \lambda S.
\end{equation}
The regularization term $S$ depends on the application, and in this case we chose the standard image entropy, or
\begin{equation}
S = \sum_{j=1}^M \frac{I_j^m}{M} \ln\left(\frac{I_j^m}{M}\right),
\end{equation}
where $M$ is the default pixel intensity value, and is set to $10^{-3}$ times the theoretical noise of the dirty map (as inferred from the visibility weights $\omega_k$). Here we set $\lambda = 0.01$.  Similar applications of {\tt uvmem} in the context of protoplanetary discs can be found, for example,  in \citet{Casassus2013Natur, 2018MNRAS.477.5104C, Casassus2019MNRAS.483.3278C,  Perez2019AJ....158...15P}.  An  advantage of {\tt uvmem} compared to more traditional imaging strategies, such as provided by the  {\tt tclean}   task in CASA, is that the effective angular resolution of the model image is  $\sim$3 times finer than the natural weights clean beam \citep[][]{2018A&C....22...16C}. This angular resolution is comparable to  uniform or super-uniform weights in {\tt tclean}, but it preserves the natural-weights point-source sensitivity.

@@

\begin{figure*}
  \includegraphics[width=\textwidth]{hot_two_E.pdf}
  \caption{Comparison of observations (top) and simulated images (bottom) at 1.65\,$\micron$ (left) and 1.3\,mm continuum (right) of the circumbinary disc orbiting V4046\,Sgr. \textit{Top left panel:} SPHERE-IRDIS \textit{H}-band image with a yellow filled circle that represents the N\_ALC\_YJH\_S coronagraph with a radius of $\sim0\farcs12$, or $\sim$8.6\,au at 72.4\,pc. \textit{Top right panel:} 1.3\,mm continuum {\tt uvmem} model image. ***NO YELLOW ELLIPSE?*** The yellow ellipse shows the size of the natural-weighted beam ($ 0\farcs062 \, \times \, 0\farcs055$), and the small orange ellipse shows an estimated {\tt uvmem} beam size ($\sim0\farcs035 \, \times \, \sim0\farcs031$ **WRONG***). The inset zooms into the central emission, and the green star marks the binary position. \textit{Bottom left panel:} synthetic image at 1.65\,$\micron$. \textit{Bottom right panel:} synthetic image at 1.3\,mm. . For all the images in the figure the colour scale is linear.}
  \label{fig:images_vs_simulated}
\end{figure*}

@@

The ring width can be measured in polar coordinates by fitting 1-D Gaussians, thus obtaining a width and centroid at each azimuth. On average, we obtained a FWHM of 2.87$\pm$0.50\,au, and a stellocentric radius of 13.32$\pm$0.26\,au (See Fig.~\ref{fig:polarring}). As the {\tt uvmem} model image has an effective angular resolution of $\sim$1/3 that of the natural-weighted beam ($0\farcs062 \,\times \, 0\farcs055$), we see that Ring13 is marginally resolved. After subtraction of the approximate {\tt uvmem} resolution ($\sim0\farcs035 \, \times \, \sim0\farcs031$), the ring width is $\sim$1.50$\pm$0.72\,au.

@@

Interestingly, the ALMA image also detects faint 1.3\,mm continuum emission near the stellar positions (See the inset in Fig.~\ref{fig:images_vs_simulated}). Since this faint central emission is larger than the angular resolution, it is probably stemming from thermal emission from  large dust grains rather directly from the stars. The main blob of this dust structure is at a estimate distance of only $0\farcs012\pm0\farcs002$, or $\sim$0.9\,au from the binary system, and may be part of an inner disc introduced in the RT model to match the SED (see Sec.~\ref{sec:model} below).

%match the small grain ring called Ring6 introduced in the RT model to match the SED (see Sec.\,\ref{sec:model} below). If so, then given that the binary phase at the time of the observations is PA=347\,$\degr$, so that the secondary lies roughly northwards of the primary, it may be that the northern side of Ring6 is shadowed, resulting in a seemingly lopsided geometry.

The scattered-light image in the top left panel of Fig.~\ref{fig:images_vs_simulated} also shows a double ring structure in the micron-sized dust distribution. The observed morphology presents an inner cavity of $\sim$10\,au in radius and two rings located at 14.10$\pm$0.01, coincident with Ring13, and 24.62$\pm$0.08\,au, coincident with Ring24, with a small gap between them at $\sim$20\,au. The observed second ring matches the inner wall of the 1.3\,mm continuum emission outer ring \citep{Ru_z_Rodr_guez_2019}. Two other important features that are present in the image are: the brightness asymmetry and the shadows projected on the disc produced by the close binary system as they eclipse each other, discovered by \citet{dOrazi}.

@@

The parametric scale height profiles for the gas and for each dust population are 
\begin{equation}
    \label{scale}
  H(r)=\chi \, H_{\circ} \, [r/r_{\circ}]^{\psi(r)},
\end{equation}
where $H_\circ$ is the scale height at $r$ = $r_\circ$, $\psi$ is the flaring index and $\chi$ is a scaling factor (in the range $0-1$) that mimics dust settling. The gas and the small dust (sd) grains have no settling, so $\chi_{\mathrm{gas}}$ = $\chi_{\mathrm{sd}}$ = 1. The radial spread of Ring13 appears about three times wider in the gas-tracing NIR observations than in the fluxes received from larger grains with ALMA. We assume that the same ratio holds in the vertical direction (due to the settling of larger grains towards the disk's midplane), leading to $\chi_{\mathrm{ld}}=0.3$.

For the vertical structure, \citet{dOrazi} found flaring angles of $\varphi$ = 6.2$\pm$0.6\,$\degr$ for the inner ring and $\varphi$ = 8.5$\pm$1.0\,$\degr$ for the outer one. Our model uses the same values, with two different flaring indices, $\psi_1$ and $\psi_2$. The separation between the two values were set at $r = 18$\,au with $\psi_1=0.15$ for Ring6 and Ring13, and $\psi_2=0.5$ for Ring24. The scale height is $H_\circ = 0.67$\,au at $r_\circ = 18$\,au.

We propose a three ringed structure to reproduce the observations. We separate the disk into four individual regions: the inner disc, Ring6, Ring13 and Ring24. The combined gas surface density profile is then given by:
\begin{equation}
  \Sigma_{\mathrm{gas}}(r) = \Sigma_{\mathrm{inner\,disc}} + \Sigma_{\mathrm{Ring6}} + \Sigma_{\mathrm{Ring13}} + \Sigma_{\mathrm{Ring24}}
\end{equation}

The inner disc follows a power law function defined by
\begin{equation}
  \Sigma_{\mathrm{inner\,disc}}(r) =\Sigma_\mathrm{c} \left(\frac{r}{R_\mathrm{c}}\right)^{-\gamma}  \, \mathrm{exp}\left[-\left(\frac{r}{R_\mathrm{c}}\right)^{2-\gamma}\right],
\end{equation}
where $R_c$ is a characteristic radius and $\gamma$ is the surface density power-law index. We used $R_c$ = 16\,au, $\Sigma_\mathrm{c} =2.8\times10^{-4}$\,$\mathrm{g\,cm^{-3}}$ and a fixed $\gamma$ = 1 as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}. Our model extends from 0.3\,au outwards, as the interior is expected to be cleared by dynamical effects of the central binary \citep{Art_Lu}

We choose to use Gaussian profiles to parameterize Ring6 and Ring13,
\begin{equation}
  \Sigma_{\mathrm{Ring}}(r) = \frac{\Sigma_\circ}{\sqrt{2 \pi} \sigma}
  \, \mathrm{exp}\left[-\frac{1}{2}\left(\frac{r-\mu}{\sigma}\right)^{2}\right],
\end{equation}
where we define constants that correspond to the centroid radii \{$\mu_{\mathrm{Ring6}}=5.5$\,au, $\mu_{\mathrm{Ring13}}=15$\,au\}, ring widths \{$\sigma_{\mathrm{Ring6}}=1$\,au, $\sigma_{\mathrm{Ring13}}=2.26$\,au\}, and normalizations \{$\Sigma_{\circ,\mathrm{Ring6}}=8\times10^{12}$\,$\mathrm{au\,g\,cm^{-3}}$, $\Sigma_{\circ,\mathrm{Ring13}}=4.2\times10^{13}$\,$\mathrm{au\,g\,cm^{-3}}$\} for both components separately.

For Ring24 we used the same power law as for the inner disc but scaled by an empirically obtained factor, $\delta_{\mathrm{sd}}$= 4.9$\times 10^4$:
\begin{equation}
  \Sigma_{\mathrm{Ring24}} = \Sigma_{\mathrm{inner\,disc}}(r)\, \delta_{\mathrm{sd}},
\end{equation}
The inner edge of Ring24 follows a different profile. Between $R_\mathrm{in}$ and $R_\mathrm{peak}$, which respectively mark  the inner edge and the location of maximum density of the outer ring, the gas density profile is multiplied by an additional factor
\begin{equation}
    \epsilon(r) = \left(\frac{ r - R_\mathrm{in}}{R_\mathrm{peak} - R_\mathrm{in}}\right)^3.
\end{equation}
This parameter allows us to model a smoother inner edge of the outer ring, with $R_\mathrm{in,gas}$ = 18.0\,au and $R_\mathrm{peak,gas}$ = 26.8\,au. This factor is also applied to the large dust population with $R_\mathrm{in,ld}$ = 24.7\,au and $R_\mathrm{peak,ld} = R_\mathrm{peak,gas}$.

@@

Since the large dust grains are less coupled to the gas, their distribution has some important differences that require a special parameterisation, with a large inner cavity, a larger gap between the rings and a break in the outer ring. We also truncated the profile of large dust grains at 64\,au. It is then defined by the sum of its two components
\begin{equation}
  \Sigma_{\mathrm{ld}}(r) = 
  \Sigma_{\mathrm{Ring13,ld}} + \Sigma_{\mathrm{Ring24,ld}}.
\end{equation}

For the inner ring, we choose a Gaussian profile parameterized with centroid radius $\mu_{\mathrm{Ring13, ld}}=13.38$\,au, ring width of $\sigma_{\mathrm{Ring13,ld}}=0.54$\,au and $\Sigma_{\circ,\mathrm{Ring13,ld}}=3.27\times10^{13}$. For Ring24 we used the same profile as for the gas, but with the difference that, in an effort to recreate the break seen in the outer ring, we choose different values for $\gamma = -4$ and $R_c$ = 39\,au between 28.6 and 35.6\,au. The surface density for large dust grains in the outer ring is thus given by
\begin{equation}
    \Sigma_{\mathrm{Ring24,ld}} = \Sigma_{\mathrm{c}} \left(\frac{r}{R_{\mathrm{c}}}\right)^{-\gamma} \exp\left[-\left(\frac{r}{R_{\mathrm{c}}}\right)^{2-\gamma}\right]\,\delta_{\mathrm{ld}}(r),
\end{equation}
where
\begin{equation}
  \delta_{\mathrm{ld}}(r) =
  \begin{cases}
  0                 & r < 24.7\text{\,au} \\
  6.13 \times10^{4} & 24.7 < r < 28.6\text{\,au} \\
  2.34 \times10^{4} & 28.6 < r < 35.6\text{\,au} \\
  2.10 \times10^{5} & 35.6 < r < 64\text{\,au.} \\
  \end{cases}
\end{equation}
Then the final density of large dust can be calculated as
\begin{equation}
\rho_{\mathrm{large-dust}}(r,z)=
\frac{\Sigma_{\mathrm{ld}}(r)}{\sqrt{2\pi} \, H(r)} \mathrm{exp}\left[-\frac{1}{2} \left(\frac{z}{H(r)}\right)^2\right] \, f_{\mathrm{ld}} \: \zeta .
\end{equation}

The two different populations of dust grains correspond to small grains, with radii ranging from 0.4 to 1.5\,$\micron$, and large dust grains, with radii from 0.4\,$\micron$ to 10\,mm. We computed the dust opacities using the {\tt bhmie} code provided in the \textsc{radmc3d} package, with a mix composed of 60\% silicate, 20\% graphite and 20\% ice.

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{allprofiles.png}
        \caption{{\bf Top:} surface density profiles for gas, large and small dust grains. {\bf Bottom:} Aspect ratio profile $h(r)= H(r)/r$. The dotted lines crossing both panels correspond to transition radii in the parametric model.}
    \label{fig:profiles}
\end{figure}

The inner radius of the model grid was set to 0.1\,au, and the outer radius to 100\,au, which is large enough for the dust disc to be undetectable. We set the values of the inclination and disc position angle to the same as obtained from the ALMA observation in Section~\ref{sec:Observations}, such that the model has an inclination of i = 32.96\,$\degr$ and a P.A. = 77.31\,$\degr$. Finally, the distance is set to d = 72.4\,pc \citep{Gaia}.

@@

The simulated image at 1.65\,$\micron$ shows a similar radial structure to the one visible in the observations, displaying a two ringed disc, where Ring6 hides under the artificial coronagraph. The visible asymmetry in the SPHERE observations is reproduced using relatively large grains, $\sim$0.4\,$\micron$, as smaller grains did not result in such strong forward scattering. As \citet{refId0} state, this forward scattering peak that is present in the observation may indicate that the dust grains in the disk surface are relatively large, suggesting that the disc is depleted of very-small grains. Interestingly, the model accurately shows the shadows described by \citet{dOrazi} that are present in the SPHERE-IRDIS image.

\begin{figure}
	\includegraphics[width=\columnwidth]{comp_fig_all_profiles_au.pdf}
    \caption{Comparison of the surface brightness profiles extracted from the deprojected synthetic images and observed \textit{H}-band and 1.3\,mm continuum images. The grey shaded area represents the radius of the artificial coronagraph used in the simulations (i.e., $\sim0\farcs 12$, or $\sim$8.6\,au at 72.4\,pc).}
    \label{fig:radprofiles}
\end{figure}

>>>>

% Abstract of the paper
\begin{abstract}
  The nearby V4046\,Sgr spectroscopic binary hosts a gas-rich disc known for its wide cavity and dusty ring.  We present high resolution ($\sim$20--50\,mas) ALMA observations of the 1.3\,mm  continuum which, combined with SPHERE-IRDIS polarized images and a well-sampled spectral energy distribution (SED), allow us to propose a physical model for the source using radiative transfer (RT) predictions. The new ALMA data reveal a very thin ring at a radius of 13.15$\pm$0.26\,au (Ring13), with a marginally resolved radial width of 2.46$\pm$0.56\,au. Ring13 is surrounded by a $\sim$10\,au-wide gap, and it is flanked by a very mm-bright outer ring (Ring24) with a sharp inner edge at 24\,au. The steeply decreasing brightness of Ring24 breaks at $\sim$35\,au into a shallow tail. In order to reproduce the SED, the model that we propose requires an inner ring at $\sim$5\,au (Ring5) composed mainly of small dust grains, hiding under the IRDIS coronagraph, and surrounding an inner circumbinary disc. The surprisingly thin Ring13 is nonetheless roughly 4 times wider than the model scale height, and could thus be long-lived. The strong near-far disc asymmetry at 1.65\,$\micron$ points at a very forward-scattering phase function, and requires grain radii of no less than 0.4\,$\micron$. The previously reported scattered-light shadow of the secondary star is also reproduced by the RADMC3D RT package. 
\end{abstract}

@@

V4046\,Sgr is a double-lined spectroscopic binary of K-type stars (K5 and K7) with very similar masses of 0.90$\pm$0.05\,M$_{\sun}$ and 0.85$\pm$0.04\,M$_{\sun}$ \citep{Rosenfeld_2012}, on a close ($a \approx 0.041$\,au), circular ($e\leq0.01$) orbit, with an orbital period of 2.42 days \citep{2000IAUS..200P..28Q}. It is a member of the $\beta$ Pictoris moving group \citep{Zuckerman_2004}, with an estimated age of 23$\pm$3\,Myr \citep{Mamajek_2014}, and its distance is 71.48$\pm$0.11\,pc \citep{gaiacollaboration2020gaia}. V4046\,Sgr hosts a massive ($\sim$0.1\,M$_{\sun}$) circumbinary disc extending to $\sim$300\,au \citep{Rosenfeld_2013, Rodriguez_2010},  rich in diverse molecular lines \citep{Kastner_2018}.

@@

Image synthesis of the ALMA continuum was performed with  the {\tt uvmem} package \citep{2006ApJ...639..951C, 2018A&C....22...16C}, which fits a non-parametric model image $I^m_j$ to the data by comparing the  observed  and model visibilities, $V^\circ_k$ and $V^m_k$, using a least-squares figure of merit $L$:
\begin{equation}
  L = \sum_{k=1}^N \omega_k  |V^\circ_k - V^m_k|^2 + \lambda S.
\end{equation}
The regularization term $S$ depends on the application, and in this case we chose the standard image entropy, or
\begin{equation}
S = \sum_{j=1}^M \frac{I_j^m}{M} \ln\left(\frac{I_j^m}{M}\right),
\end{equation}
where $M$ is the default pixel intensity value, and is set to $10^{-3}$ times the theoretical noise of the dirty map (as inferred from the visibility weights $\omega_k$). Here we set $\lambda = 0.01$.  Similar applications of {\tt uvmem} in the context of protoplanetary discs can be found, for example,  in \citet{Casassus2013Natur, 2018MNRAS.477.5104C, Casassus2019MNRAS.483.3278C,  Perez2019AJ....158...15P}.  An  advantage of {\tt uvmem} compared to more traditional imaging strategies, such as provided by the  {\tt tclean}   task in CASA, is that the effective angular resolution of the model image is  $\sim$3 times finer than the natural weights clean beam \citep[][]{2018A&C....22...16C}. This angular resolution is comparable to  uniform or super-uniform weights in {\tt tclean}, but it preserves the natural-weights point-source sensitivity.

@@

\begin{figure*}
  \includegraphics[width=\textwidth]{hot_two_E.pdf}
  \caption{Comparison of observations (top) and simulated images (bottom) at 1.65\,$\micron$ (left) and 1.3\,mm continuum (right) of the circumbinary disc orbiting V4046\,Sgr. \textit{Top left panel:} SPHERE-IRDIS \textit{H}-band image with a yellow filled circle that represents the N\_ALC\_YJH\_S coronagraph with a radius of $\sim0\farcs12$, or $\sim$8.6\,au at 71.48\,pc. \textit{Top right panel:} 1.3\,mm continuum {\tt uvmem} model image. The small orange ellipse shows an estimated {\tt uvmem} beam size ($\sim0\farcs021 \, \times \, \sim0\farcs018$). The inset zooms into the central emission, and the green star marks the binary position. \textit{Bottom left panel:} synthetic image at 1.65\,$\micron$. \textit{Bottom right panel:} synthetic image at 1.3\,mm. . For all the images in the figure the colour scale is linear.}
  \label{fig:images_vs_simulated}
\end{figure*}

@@

The ring width can be measured in polar coordinates by fitting 1-D Gaussians, thus obtaining a width and centroid at each azimuth. On average, we obtained a FWHM of 2.83$\pm$0.50\,au, and a stellocentric radius of 13.15$\pm$0.26\,au (See Fig.~\ref{fig:polarring}). As the {\tt uvmem} model image has an effective angular resolution of $\sim$1/3 that of the natural-weighted beam ($0\farcs062 \,\times \, 0\farcs055$), we see that Ring13 is marginally resolved. After subtraction of the approximate {\tt uvmem} resolution ($\sim0\farcs021 \,\times \,\sim0\farcs018$), the ring width is $\sim$2.46$\pm$0.56\,au.

@@

Interestingly, the ALMA image also detects faint 1.3\,mm continuum emission near the stellar positions (See the inset in Fig.~\ref{fig:images_vs_simulated}). Since this faint central emission is larger than the angular resolution, it is probably stemming from thermal emission from  large dust grains rather directly from the stars. The main blob of this dust structure is at a estimate distance of only $0\farcs012\pm0\farcs002$, or $\sim$0.85$\pm$0.14\,au from the binary system, and, estimating its form as a Gaussian ellipse, it has a FWHM of $\sim$1.43\,au. If this feature is caused by the presence of millimeter-size dust, its estimated mass would be around 0.12\,M$_{\earth}$. %and may be part of an inner disc introduced in the RT model to match the SED (see Sec.~\ref{sec:model} below).

The scattered-light image in the top left panel of Fig.~\ref{fig:images_vs_simulated} also shows a double ring structure in the micron-sized dust distribution. The observed morphology presents an inner cavity of $\sim$10\,au in radius and two rings located at 14.10$\pm$0.01, coincident with Ring13, and 24.62$\pm$0.08\,au, coincident with Ring24, with a small gap between them at $\sim$20\,au. The observed second ring matches the inner wall of the 1.3\,mm continuum emission outer ring \citep{Ru_z_Rodr_guez_2019}. Two other important features that are present in the image are: the brightness asymmetry, and the shadows projected on the disc by the close binary system as they eclipse each other, discovered by \citet{dOrazi}.

@@

The parametric scale height profiles for the gas and for each dust population are 
\begin{equation}
    \label{scale}
  H(r)=\chi \, H_{\circ} \, [r/r_{\circ}]^{\psi(r)},
\end{equation}
where $H_\circ$ is the scale height at $r$ = $r_\circ$, $\psi$ is the flaring index and $\chi$ is a scaling factor (in the range $0-1$) that mimics dust settling. The gas and the small dust (sd) grains have no settling, so $\chi_{\mathrm{gas}}$ = $\chi_{\mathrm{sd}}$ = 1. The radial spread of Ring13 appears two to three times wider in the gas-tracing NIR observations than in the fluxes received from larger grains with ALMA. We assume that the same ratio holds in the vertical direction (due to the settling of larger grains towards the disc's midplane), leading to $\chi_{\mathrm{ld}}=0.4$.

For the vertical structure, \citet{dOrazi} found flaring angles of $\varphi$ = 6.2$\pm$0.6\,$\degr$ for the inner ring and $\varphi$ = 8.5$\pm$1.0\,$\degr$ for the outer one. Our model uses the same values, with two different flaring indices, $\psi_1$ and $\psi_2$. The separation between the two values were set at $r = 18$\,au with $\psi_1=0.2$ for Ring5 and Ring13, and $\psi_2=0.5$ for Ring24. The scale height is $H_\circ = 0.88$\,au at $r_\circ = 18$\,au.

We propose a three ringed structure to reproduce the observations. We separate the disc into four individual regions: the inner disc, Ring5, Ring13 and Ring24. The combined gas surface density profile is then given by:
\begin{equation}
  \Sigma_{\mathrm{gas}}(r) = \Sigma_{\mathrm{inner\,disc}} + \Sigma_{\mathrm{Ring5}} + \Sigma_{\mathrm{Ring13}} + \Sigma_{\mathrm{Ring24}}
\end{equation}

The inner disc follows a power law function defined by
\begin{equation}
  \Sigma_{\mathrm{inner\,disc}}(r) =\Sigma_\mathrm{c} \left(\frac{r}{R_\mathrm{c}}\right)^{-\gamma}  \, \mathrm{exp}\left[-\left(\frac{r}{R_\mathrm{c}}\right)^{2-\gamma}\right],
\end{equation}
where $R_c$ is a characteristic radius and $\gamma$ is the surface density power-law index. We used $R_c$ = 16\,au, $\Sigma_\mathrm{c} =3.26\times10^{-4}$\,$\mathrm{g\,cm^{-3}}$ and a fixed $\gamma$ = 1 as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}. Our model extends from 0.3\,au outwards, as the interior is expected to be cleared by dynamical effects of the central binary \citep{Art_Lu}

We choose to use Gaussian profiles to parameterize Ring5 and Ring13,
\begin{equation}
  \Sigma_{\mathrm{ring}}(r) = \frac{\Sigma_\circ}{\sqrt{2 \pi} \sigma}
  \, \mathrm{exp}\left[-\frac{1}{2}\left(\frac{r-\mu}{\sigma}\right)^{2}\right],
\end{equation}
where we define constants that correspond to the centroid radii \{$\mu_{\mathrm{Ring5}}=5.5$\,au, $\mu_{\mathrm{Ring13}}=14.9$\,au\}, ring widths \{$\sigma_{\mathrm{Ring5}}=1$\,au, $\sigma_{\mathrm{Ring13}}=2.3$\,au\}, and normalizations \{$\Sigma_{\circ,\mathrm{Ring5}}=3.28$\,$\mathrm{au\,g\,cm^{-3}}$, $\Sigma_{\circ,\mathrm{Ring13}}=6 \times 10^{-1}$\,$\mathrm{au\,g\,cm^{-3}}$\} for both components separately.

For Ring24 we used the same power law as for the inner disc but scaled by an empirically obtained factor, $\delta_{\mathrm{sd}}$= 4.2$\times 10^4$:
\begin{equation}
  \Sigma_{\mathrm{Ring24}}(r) = \Sigma_{\mathrm{inner\,disc}}(r)\, \delta_{\mathrm{sd}},
\end{equation}
The inner edge of Ring24 follows a different profile. Between $R_\mathrm{in}$ and $R_\mathrm{peak}$, which respectively mark  the inner edge and the location of maximum density of the outer ring, the gas density profile is multiplied by an additional factor
\begin{equation}
    \epsilon(r) = \left(\frac{ r - R_\mathrm{in}}{R_\mathrm{peak} - R_\mathrm{in}}\right)^3.
\end{equation}
This parameter allows us to model a smoother inner edge of the outer ring, with $R_\mathrm{in,gas}$ = 18.0\,au and $R_\mathrm{peak,gas}$ = 26.4\,au. This factor is also applied to the large dust population with $R_\mathrm{in,ld}$ = 24.2\,au and $R_\mathrm{peak,ld} = R_\mathrm{peak,gas}$.

@@

Since the large dust grains are less coupled to the gas, their distribution has some important differences that require a special parameterisation, with a larger inner cavity, a larger gap between Ring13 and Ring24, and a break in the outer ring. To be consistent with the theory, Ring5 should have a small large-dust population too, but, as this ring is not visible in the ALMA observation, we added just the right mass to be undetectable by the ALMA observation. We also truncated the profile of large dust grains at 63\,au. It is then defined by the sum of its three components
\begin{equation}
  \Sigma_{\mathrm{ld}}(r) = \Sigma_{\mathrm{Ring5,ld}} + 
  \Sigma_{\mathrm{Ring13,ld}} + \Sigma_{\mathrm{Ring24,ld}}.
\end{equation}

For Ring5 and Ring13, we choose Gaussian profiles parameterized with centroid radii $\mu_{\mathrm{Ring5, ld}}=5.5$\,au and $\mu_{\mathrm{Ring13, ld}}=13.22$\,au, ring widths of $\sigma_{\mathrm{Ring5,ld}}=0.4$\,au and $\sigma_{\mathrm{Ring13,ld}}=0.85$\,au, and normalizations $\Sigma_{\circ,\mathrm{Ring5,ld}}=1.34\times10^{-4}\,\mathrm{au\,g\,cm^{-3}}$ and $\Sigma_{\circ,\mathrm{Ring13,ld}}=2.41\,\mathrm{au\,g\,cm^{-3}}$. For Ring24 we used the same profile as for the gas, but with the difference that, in an effort to recreate the break seen in the outer ring, we choose different values for $\gamma = -3.5$ and $R_c$ = 39\,au between 27.9 and 35.3\,au. The surface density for large dust grains in the outer ring is thus given by
\begin{equation}
    \Sigma_{\mathrm{Ring24,ld}}(r) = \Sigma_{\mathrm{c}} \left(\frac{r}{R_{\mathrm{c}}}\right)^{-\gamma} \exp\left[-\left(\frac{r}{R_{\mathrm{c}}}\right)^{2-\gamma}\right]\,\delta_{\mathrm{ld}}(r),
\end{equation}
where
\begin{equation}
  \delta_{\mathrm{ld}}(r) =
  \begin{cases}
  0                 & r < 24.6\text{\,au} \\
  7.19 \times10^{4} & 24.6 < r < 27.9\text{\,au} \\
  3.17 \times10^{4} & 27.9 < r < 35.3\text{\,au} \\
  2.65 \times10^{5} & 35.3 < r < 64\text{\,au.} \\
  \end{cases}
\end{equation}
Then the final density of large dust can be calculated as
\begin{equation}
\rho_{\mathrm{large\,dust}}(r,z)=
\frac{\Sigma_{\mathrm{ld}}(r)}{\sqrt{2\pi} \, H(r)} \mathrm{exp}\left[-\frac{1}{2} \left(\frac{z}{H(r)}\right)^2\right] \, f_{\mathrm{ld}} \: \zeta .
\end{equation}

The two different populations of dust grains correspond to small grains, with radii ranging from 0.3 to 1.5\,$\micron$, and large dust grains, with radii from 0.3\,$\micron$ to 10\,mm. We computed the dust opacities using the {\tt bhmie} code provided in the \textsc{radmc3d} package, with a mix composed of 60\% silicate, 20\% graphite and 20\% ice.

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{allprofiles.png}
        \caption{{\bf Top:} surface density profiles for gas, large and small dust grains. {\bf Bottom:} Aspect ratio profile $h(r)= H(r)/r$. The dashed brown line indicates the undetectable large grains in Ring5. The dotted lines crossing both panels correspond to transition radii in the parametric model.}
    \label{fig:profiles}
\end{figure}

The inner radius of the model grid was set to 0.1\,au, and the outer radius to 100\,au, which is large enough for the dust disc to be undetectable. We set the values of the inclination and disc position angle to the same as obtained from the ALMA observation in Section~\ref{sec:Observations}, such that the model has an inclination of i = 32.96\,$\degr$ and a P.A. = 77.31\,$\degr$. Finally, the distance is set to d = 71.48\,pc \citep{gaiacollaboration2020gaia}.

@@

The simulated image at 1.65\,$\micron$ shows a similar radial structure to the one visible in the observations, displaying a two ringed disc, where Ring5 hides under the artificial coronagraph. The visible asymmetry in the SPHERE observations is reproduced using relatively large grains, $\sim$0.4\,$\micron$, as smaller grains did not result in such strong forward scattering. As \citet{refId0} state, this forward scattering peak that is present in the observation may indicate that the dust grains in the disc surface are relatively large, suggesting that the disc is depleted of very-small grains. Interestingly, the model accurately shows the shadows described by \citet{dOrazi} that are present in the SPHERE-IRDIS image.

\begin{figure}
	\includegraphics[width=\columnwidth]{comp_fig_all_profiles_au.pdf}
    \caption{Comparison of the surface brightness profiles extracted from the deprojected synthetic images and observed \textit{H}-band and 1.3\,mm continuum images. The grey shaded area represents the radius of the artificial coronagraph used in the simulations (i.e., $\sim0\farcs 1$, or $\sim$7.1\,au at 71.48\,pc).}
    \label{fig:radprofiles}
\end{figure}

The simulated 1.3\,mm continuum image reproduces the two observed rings: the faint Ring13 and the brighter Ring24. The introduced Ring5 is not visible at the simulated image as its peak predicted intensities are around two times the noise in the ALMA image ($\sim1\times10^{-7}$\,Jy\,$\mathrm{beam}^{-1}$). This gives us an upper limit for the total millimeter-sized dust mass present in Ring5 of $\sim2\times10^{-5}$\,M$_{\earth}$.

As the radial profiles obtained from the simulated images of the model closely resemble those deduced from the observations (Fig.~\ref{fig:radprofiles}), we can assume that the model provides a possible approximation of the disc structure, including the dimensions of Ring13. Accordingly, taking the parametric model values for Ring13, it has a radius of 13.22\,au, a FWHM of 2.00\,au, and a scale height FWHM of the millimetre-size dust of 0.61\,au. The total dust mass of Ring13 is about 0.7\,M$_{\earth}$ in the model. In turn, our model reproduces the observations of Ring24 with peak intensity at $\sim$30\,au, and break at $\sim$36\,au. It contains a total dust mass of $\sim$44\,M$_{\earth}$. The model predictions for the millimetre-size dust population in Ring13 are close to the measurements, with only a 0.07\,au difference in the centroid location of the ring, and a 0.46\,au difference in the width estimation. Since  the  scale height of the large grains in Ring13 is  0.61\,au, and has a  measured width of 2.46\,au ***if you say measured you should give errors ***, the ring is $\sim$4.1***+-?*** times more extended radially than vertically.
